Universal Anonymous Signatures

### 2022-10-01 prism-backend/research/gsac/preliminaries-paper.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, and commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
produces the public parameters for the scheme. %
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
key pair. $\sig/\bot \gets\langle \SBCMCom^{\NIZKRel}(\vk,\overline{\smsg},
\smsg,(x,w)),\SBCMSign^\NIZKRel(\sk,\smsg,x) \rangle$ is an interactive protocol
between a user, who runs \SBCMCom and has a set of messages $\overline{\smsg}$
to be block-committed, and a signer, who owns signing key \sk; both also receive
common input a block of messages \smsg. In addition, the user knows a pair
$(x,w) \in \NIZKRel$, and proves (in zero-knowledge) knowledge of $w$ to the
signer. The output of the protocol is a signature over
$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message vector
$\overline{\smsg} \cup \smsg$. In addition, the
produced signatures must be compatible with (efficient) NIZK proofs of knowledge
of a signature, and of (arbitrary) claims over the signed (committed) messages.
An \SBCM scheme must provide one-more-forgery type of security.

>>>>

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, and commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMBlind,\SBCMSign,\SBCMUnblind,\SBCMVerify).
%
Algorithm $\parm \gets \SBCMSetup(\secpar)$ produces the public parameters for
the scheme.
% 
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing key pair.
%
$(\Ccom,\pi,r) \gets \SBCMBlind^{\NIZKRel}(\vk,\osmsg,\smsg;x',w')$ is run by a
user who wants to request a signature over $\osmsg \cup \smsg$, where only \smsg
are revealed to the signer, and $\osmsg$ are to be signed in committed form.
Moreover, \osmsg (and, possibly, $w'$) are witnesses to some statement defined
over \smsg (and, possibly, $x'$), for a relationship \NIZKRel.
%
$\SBCMbsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
signer, to produce a partial signature \SBCMbsig over a set of committed
messages and set \smsg, satisfying relation \NIZKRel.
%
$\SBCMsig \gets \SBCMUnblind^{\NIZKRel}(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg)$ is
run by the user to complete a partial signature \SBCMbsig received by the
signer, over \osmsg (committed to in \Ccom) and \smsg.
%
Finally, algorithm $1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$ verifies a
signature \sig over message vector $\osmsg \cup \smsg$.
%
In addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages. An \SBCM scheme must provide one-more-forgery type of
security.
